Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-08 acl.2016/acl2016.tex
acl paper

The standard feature functions in the phrase-based model include:
\begin{enumerate}
  \item log transforms translation model probabilities, $p_{TM}(t|s) $ and $p_{TM}(s|t)$, and word-based translation probabilities $p_w(t|s)$ and $p_w(s|t)$,
  \item log transforms of the lexicalized re-ordering probabilities,
  \item log transforms of the target language model probability $p(t)$, 
  \item a distortion penalty
  \item a phrase-penalty,
  \item a word penalty,
  \item an unknown word penalty.
\end{enumerate}
%which we have suffixed with $_{TM} $ to avoid confusion with the overall model probability $ p(t|s) $ and $ p(s|t)$.

>>>>

The standard feature functions in the phrase-based model include:
\begin{enumerate}
  \item \vspace{-2 mm} log transforms translation model probabilities, $p_{TM}(t|s) $ and $p_{TM}(s|t)$, and word-based translation probabilities $p_w(t|s)$ and $p_w(s|t)$,
  \item \vspace{-2 mm} log transforms of the lexicalized re-ordering probabilities,
  \item \vspace{-2 mm} log transforms of the target language model probability $p(t)$, 
  \item \vspace{-2 mm} a distortion penalty
  \item \vspace{-2 mm} a phrase-penalty,
  \item \vspace{-2 mm} a word penalty,
  \item \vspace{-2 mm} an unknown word penalty.
\end{enumerate}
%which we have suffixed with $_{TM} $ to avoid confusion with the overall model probability $ p(t|s) $ and $ p(s|t)$.
